An improved metric for the analysis of swarms

### 2017-09-29 paper.tex
Abstract

Both metrics are based upon the resultant internal movement of a swarm identified by analysing the changes in the inter-agent interactions. The two metrics differ in their approach to identifying the changes. The distance metric uses variations in the inter-agent distances and the new metric uses the resultant magnitudes from \textit{inter-agent vector magnitudes} which we claim offers a number of advantages over the distance metric.

@@

The magnitude based metric also identifies a swarm as expanding or cohesive.
This additional information has practical benefits for the implementation of algorithms for hetrogenious swarms.

>>>>

Both metrics are based upon the resultant internal movement of a swarm identified by analysing the changes in the inter-agent interactions. The two metrics differ in their approach to identifying the changes. The distance metric uses variations in the inter-agent distances and the new metric uses the resultant magnitudes from the agents' \textit{inter-agent vector magnitudes}  which we claim offers a number of advantages over the distance metric.

@@

In addition the magnitude based metric also identifies a swarm as expanding or cohesive.
This additional information has practical benefits for the implementation of algorithms for hetrogenious swarms.
